Nested sampling with two objective functions

### 2015-11-23 Paper/ms.tex
Updated caption
refer to correct figure

The prior $\pi(\xx)$ implies a certain prior for $L_1$ and $L_2$, which we
denote $\pi(L_1, L_2)$. An example of a prior is shown as the
probability density in Figure~\ref{fig:joint1}. The partition function
$Z(\beta_1, \beta_2)$ is a set of expected values with respect to this density.
Simple Monte Carlo sampling from $\pi$ will not work except for values of
$(\beta_1, \beta_2)$ where the canonical distribution remains similar to $\pi$.
We need a sampler that explores regions where $L_1$ and $L_2$ are high in order
to accurately estimate $Z(\beta_1, \beta_2)$.
\begin{figure}
\centering
\includegraphics[scale=0.5]{figures/joint1.pdf}
\caption{\it An example of a prior for $L_1$ and $L_2$, which is implied by
the prior $\pi(\xx)$. We have overplotted some points drawn from this prior.
\label{fig:joint1}}
\end{figure}

Our proposed algorithm (introduced in Section~\ref{sec:algorithm}) makes use
of the (two dimensional) cumulative distribution of the objective functions.
For any values $(\ell_1, \ell_2)$ of the objective functions,
the prior mass for which both $L_1 > \ell_1$ {\em and} $L_2 > \ell_2$ is:
\begin{eqnarray}
X(\ell_1, \ell_2) &=& \int \pi(L_1, L_2)
\mathds{1}\left[L_1 > \ell_1, L_2 > \ell_2 \right]
 \, dL_1 \, dL_2
\end{eqnarray}
When the prior $\pi$ is approximated with a set of $N$
particles $\{\xx_i\}_{i=1}^N$
(Monte Carlo samples ``drawn from'' $\pi$),
$X(\ell_1, \ell_2)$ can be approximated by:
\begin{eqnarray}
\hat{X}(\ell_1, \ell_2) &=&
\frac{1}{N}
\sum_{i=1}^N \mathds{1}\left[L_1(\xx_i) > \ell_1,
L_2(\xx_i) > \ell_2\right].\label{eqn:corner_count}
\end{eqnarray}
Graphically, on a plot of $L_2$ vs. $L_1$, $\hat{X}(\ell_1, \ell_2)$
is the fraction of particles in the rectangle whose upper right corner is at
$\left(\ell_1, \ell_2\right)$ (see Figure~\ref{fig:joint2} for an
example).

>>>>

The prior $\pi(\xx)$ implies a certain prior for $L_1$ and $L_2$, which we
denote $\pi(L_1, L_2)$. An example of a prior is shown as the
probability density in Figure~\ref{fig:joint1}. The partition function
$Z(\beta_1, \beta_2)$ is a set of expected values with respect to this density.
Simple Monte Carlo sampling from $\pi$ will not work except for values of
$(\beta_1, \beta_2)$ where the canonical distribution remains similar to $\pi$.
We need a sampler that explores regions where $L_1$ and $L_2$ are high in order
to accurately estimate $Z(\beta_1, \beta_2)$.
\begin{figure}
\centering
\includegraphics[scale=0.5]{figures/joint1.pdf}
\caption{\it An example of a prior for $L_1$ and $L_2$, which is implied by
the prior $\pi(\xx)$. We have overplotted 15 points drawn from this prior.
The estimated prior mass in the shaded rectangle is
$\hat{X}(3, 1.5) = 13/15 \approx 0.867$.
\label{fig:joint1}}
\end{figure}

Our proposed algorithm (introduced in Section~\ref{sec:algorithm}) makes use
of the (two dimensional) cumulative distribution of the objective functions.
For any values $(\ell_1, \ell_2)$ of the objective functions,
the prior mass for which both $L_1 > \ell_1$ {\em and} $L_2 > \ell_2$ is:
\begin{eqnarray}
X(\ell_1, \ell_2) &=& \int \pi(L_1, L_2)
\mathds{1}\left[L_1 > \ell_1, L_2 > \ell_2 \right]
 \, dL_1 \, dL_2
\end{eqnarray}
When the prior $\pi$ is approximated with a set of $N$
particles $\{\xx_i\}_{i=1}^N$
(Monte Carlo samples ``drawn from'' $\pi$),
$X(\ell_1, \ell_2)$ can be approximated by:
\begin{eqnarray}
\hat{X}(\ell_1, \ell_2) &=&
\frac{1}{N}
\sum_{i=1}^N \mathds{1}\left[L_1(\xx_i) > \ell_1,
L_2(\xx_i) > \ell_2\right].\label{eqn:corner_count}
\end{eqnarray}
Graphically, on a plot of $L_2$ vs. $L_1$, $\hat{X}(\ell_1, \ell_2)$
is the fraction of particles in the rectangle whose upper right corner is at
$\left(\ell_1, \ell_2\right)$ (see Figure~\ref{fig:joint1} for an
example).
